Initial spatial conditions in simulation models: the missing leg of sensitivity analyses?

### 2017-07-05 paper.tex

Our spatial generator applies an urban morphogenesis model (\cite{Batty2007}), which has been generalised, explored and calibrated (\cite{Raimbault2014}). \comment[FL]{il faut que les sens de tous les paramètres soient explicités avec les équations ?} In a nutshell, grids are generated through an iterative process which adds a quantity $N$ (population) at each time step, allocating it through preferential attachment characterised by its strength of attraction $\alpha$. This first growth process is then smoothed $n$ times using a diffusion process of strength $\beta$. Grids are thus generated from the combination of the values of these four meta-parameters $\alpha$, $\beta$, $n$ and $N$, in addition to the random seed. To ease our exploration, only the distribution of density is allowed to vary rather than the size of the grid, which we fix to a 50x50 square environment of 100,000 units (cf. figure \ref{fig:spatialGen}).
\comment{A detailler en incluant les equations de morphogenese}

>>>>

Our spatial generator applies an urban morphogenesis model (\cite{Batty2007}), which has been generalised, explored and calibrated (\cite{Raimbault2014}). In a nutshell, grids are generated through an iterative process which adds a quantity $N$ (population) at each time step, allocating it through preferential attachment characterised by its strength of attraction $\alpha$. More precisely, each added unit has a probability proportional to $P_i/\sum P_k$ to be added to patch $i$ with population $P_i$. At the end of each time step, this first growth process is then smoothed $n$ times using a diffusion process of strength $\beta$: each patch transmits an equal share of $\beta\cdot P_i$ to its extended neighborhood (8 surrounding patches). To avoid bord effects such as a reflexion on the border of the world, border patches diffuse to the outside.  The model stops when a fixed total population is reached. Grids are thus generated from the combination of the values of these four meta-parameters $\alpha$, $\beta$, $n$ and $N$, in addition to the random seed. To ease our exploration, only the distribution of density is allowed to vary rather than the size of the grid, which we fix to a 50x50 square environment of 100,000 units (cf. figure \ref{fig:spatialGen}). Typical value ranges for the other parameters are $\alpha\in\left[0.5,4.0\right]$, $\beta \in\left[0,0.3\right] $, $N\in \left[100,10000\right]$, $n\in\left[1,4\right]$.
\comment{A detailler en incluant les equations de morphogenese}
